simple summary of objective function for rank 1 vs rank 0

### 2017-06-20 analysis/Obj_summary.Rmd
Files commited by wflow_commit.

>>>>

## rank 0 vs rank 1

this document is based on Matthew's suggestion:

> If you simulate rank 0, and run greedy with K=1:
>
> - how often does the K=1 converge to a point mass at 0?
>
> - how often does the K=1 converge to a lower bound that is worse than the lower bound for K=0?
>
> Then you could do the same question for method =fdr (but with this penalized objective function).

### shrink method without penalty term in objective function

we find that we might need fdr method and we should use the objective funciton with penalty.[rank 0 vs rank 1](Objcheck_1.html)

### check the objective function with penalty

In this case, we check the objective funciton with penalty term, and it does monotonically increase.

### fdr method with penalty term in objective function

we can see the improvement that the proportion of P(estimated structure better than rank 0 structure) is much larger. [rank 0 vs rank 1: fdr with penalty](Objcheck_2.html)
